---
title: "Crustacean Cost-Minimization"
author: "Jason P. Dinh"
output: html_notebook
---

#Load the packages and set color codes for figures. 
```{r}
library(tidyverse)
library(readxl)
library(ggthemes)
library(cowplot)
library(ggpubr)
library(ggiraph)
library(ggiraphExtra)
library(MuMIn)
library(httr)
blue_code <- "#0073C2FF"
yellow_code <- "#EFC000FF"
```

#Download the data from Github.
```{r}
muscle_mass_data <- read.csv("https://raw.githubusercontent.com/jasonpdinh/crustacean_cost_minimization/main/Weapon_MuscleMass.csv")
```

#Filter data by species and sex. 
```{r}
UPM <- filter(muscle_mass_data, species_sex == "UPM")
AEF <- filter(muscle_mass_data, species_sex == "AEF")
AEM <- filter(muscle_mass_data, species_sex == "AEM")
AHF <- filter(muscle_mass_data, species_sex == "AHF")
AHM <- filter(muscle_mass_data, species_sex == "AHM")
```

#Filter data by species and sex. Build log-log scaling relationships and calculate residuals. 
```{r}
UPM_model <- lm(data = UPM, log10_claw_mass ~ log10_total_mass)
AEF_model <- lm(data = AEF, log10_claw_mass ~ log10_total_mass)
AEM_model <- lm(data = AEM, log10_claw_mass ~ log10_total_mass)
AHF_model <- lm(data = AHF, log10_claw_mass ~ log10_total_mass)
AHM_model <- lm(data = AHM, log10_claw_mass ~ log10_total_mass)

UPM$weapon_residual <- resid(UPM_model)
AEF$weapon_residual <- resid(AEF_model)
AEM$weapon_residual <- resid(AEM_model)
AHF$weapon_residual <- resid(AHF_model)
AHM$weapon_residual <- resid(AHM_model)
```

#Build models for Figure 2. This predicts proportion soft tissue as a function of claw mass and weapon residuals. 
```{r}
UPM_proportion_model <- lm(data = UPM, proportion_muscle ~ log10_claw_mass + weapon_residual, na.action = "na.fail")
summary(UPM_proportion_model)

AEF_proportion_model <- lm(data = AEF, proportion_muscle ~ log10_claw_mass + weapon_residual, na.action = "na.fail")
summary(AEF_proportion_model)

AEM_proportion_model <- lm(data = AEM, proportion_muscle ~ log10_claw_mass + weapon_residual, na.action = "na.fail")
summary(AEM_proportion_model)

AHF_proportion_model <- lm(data = AHF, proportion_muscle ~ log10_claw_mass + weapon_residual, na.action = "na.fail")
summary(AHF_proportion_model)

AHM_proportion_model <- lm(data = AHM, proportion_muscle ~ log10_claw_mass + weapon_residual, na.action = "na.fail")
summary(AHM_proportion_model)
```

#Calculate AICc for Figure 2 models. 
```{r}
dredge(UPM_proportion_model) #full model deltaAIC = 0.83
dredge(AEF_proportion_model) #full model deltaAIC = 2.99
dredge(AEM_proportion_model) #full model deltaAIC = 0
dredge(AHF_proportion_model) #full model deltaAIC = 1.82
dredge(AHM_proportion_model) #full model deltaAIC = 0
```

#Build Figure 2. 
```{r}
AHM_regression <- ggPredict(AHM_proportion_model, se = FALSE, interactive = FALSE) + 
  theme_few() + 
  labs(x = "log10(Claw Mass)", 
       y = "Proportion Soft Tissue", 
       col = "Weapon Residual", 
       fill = "Weapon Residual", 
       title = expression(paste(italic("Alpheus heterochaelis"), " male")), 
       subtitle = expression(paste(Delta, "AIC = 0"))) + 
  scale_y_continuous(limits = c(0.1, 0.7)) + 
  scale_x_continuous(limits = c(-2.7, -0.3)) + 
  scale_color_gradient(low = blue_code, high = yellow_code) + 
  scale_fill_gradient(low = blue_code, high = yellow_code) + 
  theme(legend.position = 'none')

AEM_regression <- ggPredict(AEM_proportion_model, se = FALSE, interactive = FALSE) + 
  theme_few() + 
  labs(x = "log10(Claw Mass)", 
       y = "Proportion Soft Tissue", 
       col = "Weapon Residual", 
       fill = "Weapon Residual", 
       title = expression(paste(italic("Alpheus estuariensis"), " male")), 
       subtitle = expression(paste(Delta, "AIC = 0"))) + 
  scale_y_continuous(limits = c(0.1, 0.7)) + 
  scale_x_continuous(limits = c(-2.7, -0.3)) + 
  scale_color_gradient(low = blue_code, high = yellow_code) + 
  scale_fill_gradient(low = blue_code, high = yellow_code)

UPM_regression <- ggPredict(UPM_proportion_model, se = FALSE, interactive = FALSE) + 
  theme_few() + 
  labs(x = "log10(Claw Mass)", 
       y = "Proportion Soft Tissue", 
       col = "Weapon Residual", 
       fill = "Weapon Residual", 
       title = expression(paste(italic("Uca pugilator"), " male")), 
       subtitle = expression(paste(Delta, "AIC = 0.83"))) + 
  scale_y_continuous(limits = c(0.1, 0.7)) + 
  scale_x_continuous(limits = c(-2.7, -0.3)) + 
  scale_color_gradient(low = blue_code, high = yellow_code) + 
  scale_fill_gradient(low = blue_code, high = yellow_code)

AHF_regression <- ggPredict(AHF_proportion_model, se = FALSE, interactive = FALSE) + 
  theme_few() + 
  labs(x = "log10(Claw Mass)", 
       y = "Proportion Soft Tissue", 
       col = "Weapon Residual", 
       fill = "Weapon Residual", 
       title = expression(paste(italic("Alpheus heterochaelis"), " female")), 
       subtitle = expression(paste(Delta, "AIC = 1.82"))) + 
  scale_y_continuous(limits = c(0.1, 0.7)) + 
  scale_x_continuous(limits = c(-2.7, -0.3)) + 
  scale_color_gradient(low = blue_code, high = yellow_code) + 
  scale_fill_gradient(low = blue_code, high = yellow_code)

AEF_regression <- ggPredict(AEF_proportion_model, se = FALSE, interactive = FALSE) + 
  theme_few() + 
  labs(x = "log10(Claw Mass)", 
       y = "Proportion Soft Tissue", 
       col = "Weapon Residual", 
       fill = "Weapon Residual", 
       title = expression(paste(italic("Alpheus estuariensis"), " female")), 
       subtitle = expression(paste(Delta, "AIC = 2.99"))) + 
  scale_y_continuous(limits = c(0.1, 0.7)) + 
  scale_x_continuous(limits = c(-2.7, -0.3)) + 
  scale_color_gradient(low = blue_code, high = yellow_code) + 
  scale_fill_gradient(low = blue_code, high = yellow_code)
```

#Put Figure 2 fgigures on a grid. 
```{r}
plot_grid(AHM_regression, AEM_regression, UPM_regression, AHF_regression, AEF_regression, 
          labels = c("a)", "b)", "c)", "d)", "e)"))
```

#Build scaling relatinoships for total claw mass, muscle mass, and inert mass (Figure 1)
```{r}
summary(lm(log10_claw_mass ~ log10_total_mass, AHM))
summary(lm(log10_muscle_mass ~ log10_total_mass, AHM))
summary(lm(log10_inert_mass ~ log10_total_mass, AHM))

AHM_scaling <- ggplot(data = AHM)  + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
             col = "gray", 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
              method = "lm", 
              col = "gray") + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
             col = yellow_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
              method = "lm", 
              col = yellow_code) + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
             col = blue_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
              method = "lm", 
              col = blue_code) + 
  theme_few() + 
  labs(x = "log10(Body Mass (g))", 
       y = "log10(Mass (g))", 
       title = expression(paste(italic("Alpheus heterochaelis"), " males")))  + 
  scale_y_continuous(limits = c(-3, 0)) + 
  scale_x_continuous(limits = c(-1.8, 0))

summary(lm(log10_claw_mass ~ log10_total_mass, AEM))
summary(lm(log10_muscle_mass ~ log10_total_mass, AEM))
summary(lm(log10_inert_mass ~ log10_total_mass, AEM))

AEM_scaling <- ggplot(data = AEM)  + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
             col = "gray", 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
              method = "lm", 
              col = "gray") + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
             col = yellow_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
              method = "lm", 
              col = yellow_code) + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
             col = blue_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
              method = "lm", 
              col = blue_code) +  
  theme_few() + 
  labs(x = "log10(Body Mass (g))", 
       y = "log10(Claw Mass (g))", 
       title = expression(paste(italic("Alpheus estuariensis"), " males")))  + 
  scale_y_continuous(limits = c(-3, 0)) + 
  scale_x_continuous(limits = c(-1.8, 0))

summary(lm(log10_claw_mass ~ log10_total_mass, UPM))
summary(lm(log10_muscle_mass ~ log10_total_mass, UPM))
summary(lm(log10_inert_mass ~ log10_total_mass, UPM))

UPM_scaling <- ggplot(data = UPM)  + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
             col = "gray", 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
              method = "lm", 
              col = "gray") + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
             col = yellow_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
              method = "lm", 
              col = yellow_code) + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
             col = blue_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
              method = "lm", 
              col = blue_code) + 
  theme_few() + 
  labs(x = "log10(Body Mass (g))", 
       y = "log10(Claw Mass (g))", 
       title = expression(paste(italic("Uca Pugilator"), " males"))) + 
  scale_y_continuous(limits = c(-3, 0)) + 
  scale_x_continuous(limits = c(-1.8, 0))

summary(lm(log10_claw_mass ~ log10_total_mass, AHF))
summary(lm(log10_muscle_mass ~ log10_total_mass, AHF))
summary(lm(log10_inert_mass ~ log10_total_mass, AHF))

AHF_scaling <- ggplot(data = AHF)   + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
             col = "gray", 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
              method = "lm", 
              col = "gray") + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
             col = yellow_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
              method = "lm", 
              col = yellow_code) + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
             col = blue_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
              method = "lm", 
              col = blue_code) + 
  theme_few() + 
  labs(x = "log10(Body Mass (g))", 
       y = "log10(Claw Mass (g))", 
       title = expression(paste(italic("Alpheus heterochaelis"), " females")))  + 
  scale_y_continuous(limits = c(-3, 0)) + 
  scale_x_continuous(limits = c(-1.8, 0))

summary(lm(log10_claw_mass ~ log10_total_mass, AEF))
summary(lm(log10_muscle_mass ~ log10_total_mass, AEF))
summary(lm(log10_inert_mass ~ log10_total_mass, AEF))

AEF_scaling <- ggplot(data = AEF)  + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
             col = "gray", 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_claw_mass), 
              method = "lm", 
              col = "gray") + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
             col = yellow_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_muscle_mass), 
              method = "lm", 
              col = yellow_code) + 
  geom_point(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
             col = blue_code, 
             alpha = 0.75, size = 2.5) + 
  geom_smooth(aes(x = log10_total_mass, 
                 y = log10_inert_mass), 
              method = "lm", 
              col = blue_code) + 
  theme_few() + 
  labs(x = "log10(Body Mass (g))", 
       y = "log10(Claw Mass (g))", 
       title = expression(paste(italic("Alpheus estuariensis"), " females"))) + 
  scale_y_continuous(limits = c(-3, 0)) + 
  scale_x_continuous(limits = c(-1.8, 0))
```

#Stitch together Figure 1
```{r}
plot_grid(AHM_scaling, AEM_scaling, UPM_scaling, AHF_scaling, AEF_scaling, 
          labels = c("a)", "b)", "c)", "d)", "e)"))
```

#Individual scaling relationships for muscle and inert mass
```{r}
summary(lm(log10_muscle_mass ~ log10_total_mass, data = UPM))
summary(lm(log10(claw_mass_after_papain) ~ log10_total_mass, data = UPM))

summary(lm(log10_muscle_mass ~ log10_total_mass, data = AEM))
summary(lm(log10(claw_mass_after_papain) ~ log10_total_mass, data = AEM))

summary(lm(log10_muscle_mass ~ log10_total_mass, data = AEF))
summary(lm(log10(claw_mass_after_papain) ~ log10_total_mass, data = AEF))

summary(lm(log10_muscle_mass ~ log10_total_mass, data = AHM))
summary(lm(log10(claw_mass_after_papain) ~ log10_total_mass, data = AHM))

summary(lm(log10_muscle_mass ~ log10_total_mass, data = AHF))
summary(lm(log10(claw_mass_after_papain) ~ log10_total_mass, data = AHF))
```
#Get percent change numbers for manuscript. 
```{r}
muscle_mass_data %>% 
  group_by(species_sex) %>% 
  summarize(max_proportion = max(proportion_muscle), 
            min_proportion = min(proportion_muscle), 
            ratio_proportion = max_proportion/min_proportion, 
            percent_difference = max_proportion - min_proportion / min_proportion)
```
#Get all data in tidy format
```{r}
log10_body_mass <- dplyr::select(muscle_mass_data, ID, log10_total_mass)

tidy_tissue <- 
  dplyr::select(muscle_mass_data, ID, claw_mass_before_papain, inert_mass, muscle_mass) %>% 
  pivot_longer(c("inert_mass", "muscle_mass"), 
               names_to = "tissue_type", 
               values_to = "mass") %>%
  mutate(species_sex = substring(ID, 1, 3), 
         log10_mass = log10(mass), 
         muscle = ifelse(tissue_type == "muscle_mass", 1, 0)) %>% 
  merge(log10_body_mass, by = "ID")

UPM_tidy <- filter(tidy_tissue, species_sex == "UPM")
AEF_tidy <- filter(tidy_tissue, species_sex == "AEF")
AEM_tidy <- filter(tidy_tissue, species_sex == "AEM")
AHF_tidy <- filter(tidy_tissue, species_sex == "AHF")
AHM_tidy <- filter(tidy_tissue, species_sex == "AHM")
```

#Test if scaling slopes vary by tissue type.
```{r}
summary(lm(log10_mass ~ log10_total_mass*muscle, data = UPM_tidy))
summary(lm(log10_mass ~ log10_total_mass*muscle, data = AHF_tidy))
summary(lm(log10_mass ~ log10_total_mass*muscle, data = AHM_tidy))
summary(lm(log10_mass ~ log10_total_mass*muscle, data = AEF_tidy))
summary(lm(log10_mass ~ log10_total_mass*muscle, data = AEM_tidy))
```
#Get AICc to see if slopes vary by tissue types. 
```{r}
dredge(lm(log10_mass ~ log10_total_mass*muscle, data = UPM_tidy, na.action = "na.fail"))
dredge(lm(log10_mass ~ log10_total_mass*muscle, data = AHF_tidy, na.action = "na.fail"))
dredge(lm(log10_mass ~ log10_total_mass*muscle, data = AHM_tidy, na.action = "na.fail"))
dredge(lm(log10_mass ~ log10_total_mass*muscle, data = AEF_tidy, na.action = "na.fail"))
dredge(lm(log10_mass ~ log10_total_mass*muscle, data = AEM_tidy, na.action = "na.fail"))
```


